On Secure Delegation of SampBQP with a Classical Client

### 2020-02-10 bqp.tex
Implement more Skype call comments

\Ethan{Use only pk, sk and combine evk into pk}

@@

Now we state our results of compiling $\PiMF$ using $\mathsf{QHE}$:
\Ethan{We state our construction of blind QPIP 1 for BQP by compiling...}

@@

	\begin{enumerate}
		\item The verifier generates $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$.
			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
			It also sends $pk$ to the prover.
		\item The prover homomorphically evaluates $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\cPblind{1}(pk, ct_x)=\QEval_{pk}(\cPMF{1}, ct_x)$.
			It sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier generates $\Lambda\leftarrow\cVMF{2}(x)$,
			$\Lambda'\leftarrow\cM_\QHE(\Lambda)$,
			$ct_w\leftarrow\Lambda'(\sigma)$,
			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
			and $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
			It outputs $o$.
	\end{enumerate}
\end{protocol}

@@

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.

	Observe the experiments $A$ and $B$ \Ethan{TODO} are identical except...

    \Ethan{See google docs; remove the displayed math above and say in words}
	By inspection, the only difference between the experiments is how $w$ is obtained from $\sigma$.
	By \cref{decodeMeasureOrder}, the two ways are equivalent.
	\Ethan{Here finish the proof by contradiction. Something about epsilon.}
\end{prf}

@@

$k$ has the additional properties to not leak information on $\Lambda'$, so the compliation preserves blindness. \Ethan{How to make this more rigorous?}

@@

\begin{thm}
	\cref{proto:repQPIP0BQP} has negligible completeness and soundness and is blind.
\end{thm}
\begin{prf}
	See \cite{parallelrep, alagic2019twomessage}
\end{prf}

>>>>

@@

Now we state our construction of blind QPIP 1 for BQP by compiling $\PiMF$ using $\QHE$:

@@

	\begin{enumerate}
		\item The verifier generates $(pk, sk)\leftarrow\mathsf{QHE.Keygen}(1^n, 1^d)$, where $d$ is the depth of the circuit corresponding to $\cPMF{1}(x)$.
			It then generates and sends $ct_x\leftarrow\mathsf{QHE.Enc}_{pk}(x)$ to the prover.
			It also sends $pk$ to the prover.
		\item The prover computes $\sigma\leftarrow\cPblind{1}$ by homomorphically evaluating $\cPMF{1}$ on input $ct_x$, generating $\sigma\leftarrow\QEval_{pk}(\cPMF{1}, ct_x)$.
			It sends $\sigma$ to the verifier qubit-by-qubit.
		\item The verifier generates $\Lambda\leftarrow\cVMF{2}(x)$,
			$\Lambda'\leftarrow\cM_\QHE(\Lambda)$,
			$ct_w\leftarrow\Lambda'(\sigma)$,
			$w\leftarrow\widehat{\mathsf{QHE.Dec}_{sk}}(ct_w)$,
			and $o\leftarrow\cVMF{3}(x, \Lambda, w)$.
			It outputs $o$.
	\end{enumerate}
\end{protocol}

@@

	We now prove that $\PMFstar$ in fact violates the soundness of $\PiMF$.
	Let $\cP_\blind^*$ denote the action $\Pblindstar$ takes to produce $\sigma$ from $ct_x$.
	Observe the experiments $A$ and $B$ \Ethan{TODO} are identical except how $w$ is obtained from $\sigma$.
	\Ethan{TODO Make more precise}
	By \cref{decodeMeasureOrder}, the two ways are equivalent.
	\Ethan{Here finish the proof by contradiction. Something about epsilon.}
\end{prf}

@@

For blindness, recall that the prover receives $ct_x = Enc(x), evk, k, c$ from the verifier. Blindness follows by the semantic security of QFHE and the fact that k computationally hides the basis choice $\Lambda$.
\Ethan{This sentence is from google docs so keep it around}

@@

\begin{thm}
	\cref{proto:repQPIP0BQP} has negligible completeness and soundness.
\end{thm}
\begin{prf}
	\Ethan{Don't open separate proof env}
	See \cite{parallelrep, alagic2019twomessage}
\end{prf}
